Identifying regime transitions for water governance at a basin scale

### 2022-05-31 paper/main/01_introduction.tex
fix(cover-letter): add cover letter text, fix figure1's caption

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		Framework for identifying the water governance regimes in transitions of a hydrosocial cycle. Water stress (S), purpose of water services (P) and water allocation (A) are three aspects to be considered (\textbf{A.}). Along hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance, such as: construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2), water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
		Therefore, the methonology is to combine three aspects' corresponding indicator, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
	}
	\label{fig:framework}
\end{figure*}

>>>>

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		Identifying the water governance regimes in transitions of a hydrosocial cycle with an integrated water governance index (IWGI). Water stress (S), purposes of water services (P), and water allocation (A) are three aspects to be considered (\textbf{A.}). Along with hydrosocial-cycle transitions, a human-dominated regime influences these aspects of water governance. For example, the construction of reservoirs (1) aims to alleviate water stress; growth of energy and industry (2); water-lead intensive agriculture (3); conveyance system (4) controls water allocation.
		Therefore, the methodology is to combine three aspects' corresponding indicators, and then an abrupt change of the IWGI can indicate a regime shift in water governance (\textbf{B.}).
	}
	\label{fig:framework}
\end{figure*}
